---
title: "RMark_week 6.2"
author: "Sejordan"
date: "3/3/2021"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

# **Introduction**   
Here is some code for making a table and a plot of the Palmer Penguin data using species, body mass, and island.  

# **Libraries**  
First we need to load these 4 libraries:
```{r}
library(tidyverse)
library(palmerpenguins)
library(here)
library(kableExtra)
```


# **Table**  
Make a table:
```{r}
penguins %>%
  group_by(species) %>%
  summarise(body_mass_g = mean(body_mass_g, na.rm = TRUE)) %>%
  kbl() %>% #puts specified data into a table
  kable_classic() #makes table look publication quality
```

# **Plot**  
Make a plot:
```{r label, fig.cap="Figure 1. Body Mass of 3 Species of Palmer Penguins at 3 Islands", fig.align="center"}
ggplot(data=penguins,
       mapping = aes(x = factor(island), #make island a factor
                     y = body_mass_g, color = island)) + #color code by island
          geom_boxplot(show.legend = FALSE)+ #make boxplots
          facet_wrap(~species)+ #facet wrap by species
       labs(x = "Island",  
         y = "Body Mass (g)")+ #label axes
       theme_bw()+ #set up background theme
        theme(axis.title = element_text(size=14, color="black"))+ 
        guides(color = FALSE)+
        scale_color_viridis_d() #make friendly colors
        ggsave(here("Week_6","Output","penguin.png"),
         width = 7, height = 5) #saves plot to output folder
```

# **Discussion**  
Adelie was the only species found on all three islands, and there does not appear to be much variation in mass among islands. Chinstrap was found only on Dream Island, and does not appear to have a different mass than Adelie. Gentoo was found only on Biscoe Island and has on avaerage a larger mass than the other two penguin species.